---
title: "p8105_hw1_ml4239"
output: github_document
Author: "Man Luo"
Date: 2018-09-19
---
#**Problem_1**
##Create a data frame named as problem_1_data_frame
```{r}
library(tidyverse)
```

```{r}
set.seed(1)
problem_1_data_frame = tibble(
  uniform_sample = runif(10, min = 0, max = 5),
  vec_logic = uniform_sample > 2,
  vec_character = c("x","y","z","z","z","y","x","z","y","x"),
  vec_factor = factor(c("I","you","she","he", "it", "they", "ze", "he", "xe", "none"))
)
```

##Take the mean of each variable in dataframe 'problem_1_data_frame'.

```{r}
mean(problem_1_data_frame$uniform_sample)
mean(problem_1_data_frame$vec_logic)
mean(problem_1_data_frame$vec_character)
mean(problem_1_data_frame$vec_factor)
```
The mean of random sample and logical vector work.  
The mean of character vector and factor vector do not work.
Because the variables in the last two are not numeric or logical.

##Convert variables from one type to another
+ Applies the as.numeric function to the logical, character, and factor variables 
```{r eval = FALSE}
as.numeric(problem_1_data_frame$vec_logic)
as.numeric(problem_1_data_frame$vec_character)
as.numeric(problem_1_data_frame$vec_factor)
```
The variables in vec_logic convert to "0"&"1" from "Flase"&"True".  
The variables in vec_charater convert to NA.   
The variables in vec_factor convert to different numbers according to their levels (in alphabet). 

+ Convert character variable from character to factor to numeric; similarly, convert factor variable from factor to character to numeric. 

```{r}
as.numeric(as.factor(problem_1_data_frame$vec_character))
as.numeric(as.character(problem_1_data_frame$vec_factor))
```
The variables from character variable from character to factor to numeric are convert to numbers according to the factor level.  
The variables from factor variable from factor to character to numeric are convert to NA.


#**Problem_2**
##Create a data frame named problem_2_data_frame
```{r}
problem_2_data_frame = tibble(
  x = rnorm(1000),
  y = rnorm(1000),
  vec_logic_2 = x + y > 0,
  vec_numeric_2 = as.numeric(vec_logic_2),
  vec_factor_2 = as.factor(vec_logic_2)
)
```
The size of the dataset is  `r object.size(problem_2_data_frame)`  
The mean of x is `r mean(problem_2_data_frame$x)`  
The median of x is `r median(problem_2_data_frame$x)`  
The proportion of cases for which the logical vector is `TRUE` is `r sum(problem_2_data_frame$vec_logic_2 == "TRUE")/1000`